---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE,message=F,warning=F}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(tidyverse)
```

# epidemos

*epidemos* is a collection of useful tools for epidemiological analysis that is still work in progress. Up to know, the published beta version includes functions primarily focussing on the data collection/scraping process. In order to facilitate that process, *epidemos* provides APIs to different public sources of large epidemiological datasets such as the *Global Health Data Exchange (GHDx)*. 

## Installation

You can install `epidemos` from github via:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("schliebs/epidemos")
library(epidemos)
```

# Example functions

## Download Raw Data

Download ghdx US county level data from 1980 - 2014

```{r,eval = F}
library(epidemos)

downloadHealthData(dataset = "ghdx",
                   folder = "rawdata")

```


## Clean Data

Unzip and clean ghdx data

```{r,echo = FALSE}

```



